\begin{thebibliography}{9} % Bibliography - this is intentionally simple in this template

\bibitem[Bondy et al, 1976]{BondyMurty:1976}
    Bondy, J.~A. and Murty, U.~S.~R (1976).
    \newblock Graph Theory With Applications,
    \newblock ch. 1-2,
    \newblock 1. Edition,
    \newblock The Macmillan Press Ltd., Great Britain
    
\bibitem[Corey et al, 1995]{Corey:1995}
    Corey, E.~J. and Cheng X-M. (1995).
    \newblock The Logic of Chemical Synthesis,
    \newblock 1. Edition,
    \newblock Wiley-Interscience, New York.
    
\bibitem[Cormen et al, 2009]{Cormen:2009}
    Cormen, T.~H.; Leiserson, C.~E.; Rivest, R.~L. and Stein, C. (2009).
    \newblock Introduction to Algorithms,
    \newblock ch. B.5,
    \newblock 3. Edition,
    \newblock The MIT Press, Cambridge, Massachusetts.

\bibitem[May et al, 1976]{MayRudd:1976}
    May, D. and Rudd, D.~F. (1976).
    \newblock Development of Solvay Clusters of Chemical Reactions,
    \newblock {\em Chemical Engineering Science}, 31:59--69,
    \newblock Pergamon Press, Great Britain.

\bibitem[Nilsson, 2012]{Nilsson:2012}
    Nilsson, J.~F. (2012).
    \newblock Computerized Means-End Reasoning Applied to Chemical Retro-Synthesis,
    \newblock {\url{www.campusnet.dtu.dk}}
    
\bibitem[NIOSH, 2014]{NIOSH:2014}
    \newblock Hydrogen chloride,
    \newblock{\url{http://www.cdc.gov}},
    \newblock 4$^{th}$ December 2014.
    \newblock{\url{http://www.cdc.gov/niosh/idlh/7647010.html}},
    \newblock (Retrieved: 16$^{th}$ June 2016).

\bibitem[Rudd, 1976]{Rudd:1976}
    Rudd, D.~F. (1976).
    \newblock Accessible Designs in Solvay Cluster Synthesis,
    \newblock {\em Chemical Engineering Science}, 31:701--703,
    \newblock Pergamon Press, Great Britain.

\bibitem[Russell et al, 1995]{RussellNorvig:1995}
    Russell, S. and Norvig, P. (1995).
    \newblock Artificial Intelligence A Modern Approach,
    \newblock ch. 3,
    \newblock 3. Edition,
    \newblock Pearson Education, Inc., United States of America.

\bibitem[Wikipedia, 2016]{Wiki:2016}
    \newblock Reaction scheme of the Leblanc process,
    \newblock {\url{https://en.wikipedia.org/wiki/Leblanc_process}},
    \newblock 17$^{th}$ January 2016.
    \newblock {\url{https://en.wikipedia.org/wiki/Leblanc_process#/media/File:Leblanc_process_reaction_scheme.svg}},
    \newblock (Retrieved: 13$^{th}$ April 2016).
\end{thebibliography}